The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-12 Writeup/paper_v3.tex
Comment out conversation about arXiv

\rachel{Need to fix arXiv references so that they show up properly
  with e-print number.}
\arun{I thought it has to do with MNRAS format.}
\claire{Maybe Rachel knows a smart trick here, but I think you have to include the arxiv numbers in the .bbl file by hand as the .bib file doesn't do them correctly... MNRAS wants this format: Smith P. et al., 2013, preprint (arXiv:0123.4567).}
\rachel{No, I know of no smart trick.  My approach is that once I
  think the paper is ready to submit, I edit the .bbl file.  It would
  be lovely if MNRAS was to fix its .bst file to address this and
  other problems, but they won't.  Arun, once you're doing this, the
  other thing to do is check if any of the 2014 preprints have been
  published, because if they have then we should refer
to them (obviously, no need to check old references like Albrecht et
al 2006, Laureijs et al 2012, etc.).}

>>>>

% \rachel{Need to fix arXiv references so that they show up properly
%   with e-print number.}
% \arun{I thought it has to do with MNRAS format.}
% \claire{Maybe Rachel knows a smart trick here, but I think you have to include the arxiv numbers in the .bbl file by hand as the .bib file doesn't do them correctly... MNRAS wants this format: Smith P. et al., 2013, preprint (arXiv:0123.4567).}
% \rachel{No, I know of no smart trick.  My approach is that once I
%   think the paper is ready to submit, I edit the .bbl file.  It would
%   be lovely if MNRAS was to fix its .bst file to address this and
%   other problems, but they won't.  Arun, once you're doing this, the
%   other thing to do is check if any of the 2014 preprints have been
%   published, because if they have then we should refer
% to them (obviously, no need to check old references like Albrecht et
% al 2006, Laureijs et al 2012, etc.).}
